Pre-registered Analyses

### 2020-08-03 pre-registered_analyses.Rmd
zoe's feedback

```{r read_dat}
# read in data from csv
LIs <- read.csv("LIs.csv", na.strings = c("NA", ""))
# then we exclude those who we do not have full datasets for 
LIs <- subset(LIs, exclude== 0)
```

>>>>

```{r read_dat}
# read in data from csv
LIs <- read.csv('https://osf.io/x5jd2/download',stringsAsFactors = F)
# then we exclude those who we do not have full datasets for 
LIs <- subset(LIs, exclude== 0)
LIs %>%
    summarize(avg = mean(age), n = n(), sd = sd(age))
# second, show gender count for the whole population
allsum %>%
  group_by(gender) %>%
    summarize(n = n())
# fourth, show handedness
allsum %>%
  group_by(handedness, gender) %>%
    summarize(n = n())
```
